Trends of SDR in Thessaloniki

### 2023-08-30 Article.Rmd
Commit 2023-08-30 18:14

.... cite paper about low elevation SDR .....

The relative position of the Sun in the sky, seem to be a major drive of the attenuation of SDR, as it is affect

... Aerosols and clouds ...

We group the anomaly data in $1^\circ$ SZA bins, and calculated the overall trend for each bin

Analyzing the long term trends of SDR to bins of SZA, we can see the contribution of the geometry and time in a diurnal level (Figures\ \ref{fig:szatrends}a and \ref{fig:szatrends}b). Although there is a seasonal distribution of SZA than in not presented here.

>>>>

The relative position of the Sun in the sky, is a major drive of the attenuation of SDR reaching the ground, as it is affected by the radiation path in the atmosphere and possible human activities in urban environment emitting aerosols [@Wang2021].
In order to estimate the contribution of the SZA, we group the anomaly data in $1^\circ$ SZA bins, and calculated the overall trend for each bin (Figures\ \ref{fig:szatrends}a and \ref{fig:szatrends}b).
Although there is a seasonal change of SZA limits than is not represented here, the brightening effect of SDR is stronger for All-sky and Clear-sky condition for low Sun elevation angles.
